---
title: "D3 example"
---

I first [look up D3 on npm](https://www.npmjs.com/package/d3). We'll get the package from cdn.jsdelivr.net, like they demonstrate in their documentation. However:

* The latest version when I write this is 7.8.0, so for reproducibility I will specifically use this version.
* Using `jsandr::depend` includes the package directly in the HTML file, making it self-contained. When someone views the HTML file they will not need access to cdn.jsdelivr.net. 

```{r setup}
library(jsandr)

depend("https://cdn.jsdelivr.net/npm/d3@7.8.0")
```

Send some data to Javascript to play with.

```{r}
let(mtcars=mtcars)
```

Now we can write some Javascript.

```{js}
function update() {
    let minMpg = parseFloat( document.getElementById("minMpg").value );
    
    let filteredCars = mtcars.filter(d => d.mpg>=minMpg);
    
    let xScale = d3.scaleLinear()
        .domain([0,35])
        .range([150,450]);
        
    let yScale = d3.scaleBand()
        .domain(filteredCars.map(d=>d._row))
        .range([0,450])
        .padding(0.2);
    
    d3.select("#xAxis")
        .attr("transform",`translate(0,${yScale.range()[1]})`)
        .call( d3.axisBottom(xScale) );
    
    d3.select("#yAxis")
        .attr("transform",`translate(${xScale.range()[0]},0)`)
        .call( d3.axisLeft(yScale).tickSizeOuter(0) );
    
    d3.select("#bars")
        .selectAll("rect")
        .data(filteredCars, d=>d._row)
        .join("rect")
        .attr("fill", "#88f")
        .attr("x", xScale(0))
        .attr("width", d=>xScale(d.mpg)-xScale(0))
        .attr("y", d=>yScale(d._row))
        .attr("height", yScale.bandwidth());
}

window.addEventListener("load", update);
```

## Miles Per Gallon

Minimum MPG: <input type="number" id="minMpg" min="0" max="35" step="5" value="10" onchange="update()">

<svg id="output" width="500" height="500">
    <g id="bars"></g>
    <g id="xAxis"></g>
    <g id="yAxis"></g>
</svg>
