---
title: "Crosstalk + Plotly + Javascript example"
---

Here I demonstrate:

* `let()` and `let1()` to send data to Javascript.
* `talkToPlotly()` to tweak plotly-crosstalk interaction.
* Accessing a crosstalk selection from Javascript.
* Laying out widgets using a `display: grid` styled div.

First create some widgets:

```{r warning=FALSE,message=FALSE}
library(crosstalk)
library(htmltools)
library(plotly)
library(tidyverse)
library(geozoo)
library(langevitour)
library(jsandr)

# Example dataset
df <- as.data.frame(conic.spiral.nautilus(n=5000, b=1)$points)

# We can enable crosstalk between various widgets by
# using a SharedData object in place of a data frame.
shared <- SharedData$new(df)

p1 <- ggplot(shared)+aes(x=V2,y=V1)+geom_point(size=0.5)
p2 <- ggplot(shared)+aes(x=V2,y=V3)+geom_point(size=0.5)

# Convert ggplot to plotly with talkToPlotly. 
w1 <- talkToPlotly(p1, width="400", height="400")
w2 <- talkToPlotly(p2, width="400", height="400")

# Just for fun, use my widget too.
wLangevitour <- langevitour(df, link=shared, width="500", height="600")

# Tell Javascript the crosstalk group name.
let1(groupName = shared$groupName())
```

Javascript code:

```{js}
// The crosstalk group name lets us interact with selections and filters.
let handle = new crosstalk.SelectionHandle();
handle.setGroup(groupName);

// Idempotent update function.
// Make sure the displayed text matches the selection.
function update() {
    document.getElementById("out").innerText = 'Javascript says: You\'ve selected '+(handle.value||[]).length+' points.';
}

// update function should be called when selection changes.
handle.on("change", update);

// update function should be called initially when the page is loaded.
window.addEventListener("load", update);
```

Show the widgets, and provide an output element for the Javascript:

```{r}
browsable(div(
    style="display: grid; grid-template-columns: 0fr 1fr;",
    w1,            w2,
    wLangevitour,  div(id="out")
    ))
```

* Why `browsable(...)`? It's not really necessary here, but in an interactive session it will make the HTML appear in the RStudio viewer pane or in a web browser, rather than the console.

* What is the style doing? It sets the div up to display using "grid" layout. Since `grid-template-columns:` has two items, there will be two columns. The numbers `0fr` and `1fr` dictate the proportion of leftover space allocated to each column. You could also use other CSS units here such as `px`.
